Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-07-24 manuscript.tex
address and hacky fix to overflow

\author[1\authfn{1}*]{Christoph Wehmeyer}
\author[1\authfn{1}]{Martin K. Scherer}
\author[1\authfn{1}]{Tim Hempel}
\author[2]{Brooke E. Husic}
\author[1]{Simon Olsson}
\author[1*]{Frank Noé}
\affil[1]{Department of Mathematics and Computer Science, Freie Universität Berlin, Arnimallee 6, 14195 Berlin, Germany}
\affil[2]{Department of Chemistry, Stanford University, Stanford, California 94305, USA}

@@

In short, the workflow consists of:
\begin{itemize}
	\item extracting molecular features from the raw data (01),
	\item transforming those features into a suitable, low-dimensional subspace (02),
	\item discretizing the low-dimensional subsets into a state decomposition (02),
	\item estimating a maximum likelihood or Bayesian MSM from the discrete trajectories and performing validation tests (03),
	\item analyzing the stationary and kinetic properties of the MSM (04),
	\item finding metastable macrostates and applying transition path theory (TPT) to identify the pathways of conformation change (05),
	\item computing expectation values for experimental observables (06), and
	\item coarse-graining the model using a hidden Markov model approach (07).
\end{itemize}

>>>>

\author[1\authfn{1}*]{Christoph Wehmeyer}
\author[1\authfn{1}]{Martin K. Scherer}
\author[1\authfn{1}]{Tim Hempel}
\author[2]{Brooke E. Husic}
\author[1]{Simon Olsson}
\author[1*]{Frank Noé}
\affil[1]{Department of Mathematics and Computer Science, Freie Universität Berlin, Arnimallee 6, 14195 Berlin, Germany}
\affil[2]{Department of Chemistry, Stanford University, 333 Campus Drive, Stanford, California 94305, USA}

@@

In short, the workflow consists of:
\begin{itemize}
	\item extracting molecular features from the raw data (01),
	\item transforming those features into a suitable, low dimensional subspace (02),
	\item discretizing the low-dimensional subsets into a state decomposition (02),
	\item estimating a maximum likelihood or Bayesian MSM from the discrete trajectories and performing validation tests (03),
	\item analyzing the stationary and kinetic properties of the MSM (04),
	\item finding metastable macrostates and applying transition path theory (TPT) to identify the pathways of conformation change (05),
	\item computing expectation values for experimental observables (06), and
	\item coarse-graining the model using a hidden Markov model approach (07).
\end{itemize}
